### 2022-12-28 output/summary_statistics/tables/balance_table.tex
About to revamp DiD observed periodS

\begin{tabular}{llcccc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Cases Won by Defendant}} & \multicolumn{2}{c}{\textit{Cases Won by Plaintiff}} \\
 &  & Mean & N & Mean & N \\
Panel & Variable &  &  &  &  \\
\midrule
\multirow[c]{8}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 4090 & 0.12 & 11921 \\
 & For cause (transfer) & 0.01 & 4090 & 0.01 & 11921 \\
 & Foreclosure & 0.01 & 4090 & 0.03 & 11921 \\
 & Foreclosure (transfer) & 0.00 & 4090 & 0.00 & 11921 \\
 & No cause & 0.12 & 4090 & 0.10 & 11921 \\
 & No cause (transfer) & 0.01 & 4090 & 0.00 & 11921 \\
 & Non-payment of rent & 0.69 & 4090 & 0.72 & 11921 \\
 & Non-payment of rent (transfer) & 0.03 & 4090 & 0.01 & 11921 \\
\cline{1-6}
\multirow[c]{4}{4cm}{\textit{Panel B: Case Resolution}} & Case defaulted & 0.00 & 4090 & 0.67 & 11921 \\
 & Case involuntarily dismissed & 0.99 & 4090 & 0.00 & 11921 \\
 & Case heard & 0.01 & 4090 & 0.19 & 11921 \\
 & Case mediated & 0.00 & 4090 & 0.00 & 11921 \\
\cline{1-6}
\multirow[c]{5}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.20 & 4090 & 0.07 & 11921 \\
 & Plaintiff has an attorney & 0.79 & 4090 & 0.81 & 11921 \\
 & Defendant is an entity & 0.01 & 4090 & 0.01 & 11921 \\
 & Plaintiff is an entity & 0.63 & 4090 & 0.67 & 11921 \\
 & Money judgment & 57.56 & 4090 & 3444.31 & 11921 \\
\cline{1-6}
\multirow[c]{5}{4cm}{\textit{Panel D: Assessor Records From Post-Filing F.Y.}} & Total property value & 6478531.48 & 1256 & 8995455.63 & 3992 \\
 & Building value & 1605427.57 & 1256 & 2352344.15 & 3992 \\
 & Land value & 61247.49 & 1256 & 100993.11 & 3992 \\
 & Other value & 8138231.73 & 1256 & 11437647.57 & 3992 \\
 & Units & 41.23 & 1256 & 42.09 & 3992 \\
\cline{1-6}
\multirow[c]{9}{4cm}{\textit{Panel E: Zestimates Around Last Docket Date}} & Five years before latest docket date & 245078.62 & 957 & 275426.28 & 2603 \\
 & Four years before latest docket date & 265248.64 & 977 & 294572.61 & 2635 \\
 & Three years before latest docket date & 308529.26 & 992 & 317382.82 & 2706 \\
 & Two years before latest docket date & 330329.21 & 998 & 346565.14 & 2709 \\
 & One year before latest docket date & 336544.68 & 1002 & 364931.93 & 2715 \\
 & Latest docket date & 364629.48 & 991 & 391919.00 & 2701 \\
 & One year after latest docket date & 412421.05 & 1045 & 440748.11 & 2796 \\
 & Two years after latest docket date & 450898.44 & 801 & 509321.48 & 2493 \\
 & Three years after latest docket date & 485688.38 & 441 & 512215.31 & 1613 \\
\cline{1-6}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llcccc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Cases Won by Defendant}} & \multicolumn{2}{c}{\textit{Cases Won by Plaintiff}} \\
 &  & Mean & N & Mean & N \\
Panel & Variable &  &  &  &  \\
\midrule
\multirow[c]{8}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 4090 & 0.12 & 11921 \\
 & For cause (transfer) & 0.01 & 4090 & 0.01 & 11921 \\
 & Foreclosure & 0.01 & 4090 & 0.03 & 11921 \\
 & Foreclosure (transfer) & 0.00 & 4090 & 0.00 & 11921 \\
 & No cause & 0.12 & 4090 & 0.10 & 11921 \\
 & No cause (transfer) & 0.01 & 4090 & 0.00 & 11921 \\
 & Non-payment of rent & 0.69 & 4090 & 0.72 & 11921 \\
 & Non-payment of rent (transfer) & 0.03 & 4090 & 0.01 & 11921 \\
\cline{1-6}
\multirow[c]{4}{4cm}{\textit{Panel B: Case Resolution}} & Case defaulted & 0.00 & 4090 & 0.67 & 11921 \\
 & Case involuntarily dismissed & 0.99 & 4090 & 0.00 & 11921 \\
 & Case heard & 0.01 & 4090 & 0.19 & 11921 \\
 & Case mediated & 0.00 & 4090 & 0.00 & 11921 \\
\cline{1-6}
\multirow[c]{5}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.20 & 4090 & 0.07 & 11921 \\
 & Plaintiff has an attorney & 0.79 & 4090 & 0.81 & 11921 \\
 & Defendant is an entity & 0.01 & 4090 & 0.01 & 11921 \\
 & Plaintiff is an entity & 0.63 & 4090 & 0.67 & 11921 \\
 & Money judgment & 57.56 & 4090 & 3444.31 & 11921 \\
\cline{1-6}
\multirow[c]{5}{4cm}{\textit{Panel D: Assessor Records From Post-Filing F.Y.}} & Total property value & 6478531.48 & 1256 & 8995455.63 & 3992 \\
 & Building value & 1605427.57 & 1256 & 2352344.15 & 3992 \\
 & Land value & 61247.49 & 1256 & 100993.11 & 3992 \\
 & Other value & 8138231.73 & 1256 & 11437647.57 & 3992 \\
 & Units & 41.23 & 1256 & 42.09 & 3992 \\
\cline{1-6}
\multirow[c]{9}{4cm}{\textit{Panel E: Zestimates Around Last Docket Date}} & Five years before latest docket date & 255601.88 & 1019 & 267829.81 & 2904 \\
 & Four years before latest docket date & 278440.18 & 1035 & 286996.41 & 2939 \\
 & Three years before latest docket date & 297578.04 & 1052 & 313182.84 & 3015 \\
 & Two years before latest docket date & 332743.89 & 1055 & 341145.74 & 3016 \\
 & One year before latest docket date & 338598.45 & 1058 & 360142.85 & 3018 \\
 & Latest docket date & 373816.17 & 1044 & 387035.91 & 2993 \\
 & One year after latest docket date & 419391.34 & 1086 & 431642.67 & 3087 \\
 & Two years after latest docket date & 446124.50 & 824 & 491836.71 & 2726 \\
 & Three years after latest docket date & 482504.08 & 455 & 508987.34 & 1793 \\
\cline{1-6}
\bottomrule
\end{tabular}

### 2022-12-28 output/summary_statistics/tables/summary_statistics.tex
About to revamp DiD observed periodS

\begin{tabular}{llccc}
\toprule
 &  & Mean & S.D. & N \\
Panel & Variable &  &  &  \\
\midrule
\multirow[c]{8}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 0.32 & 40,735 \\
 & For cause (transfer) & 0.01 & 0.08 & 40,735 \\
 & Foreclosure & 0.02 & 0.14 & 40,735 \\
 & Foreclosure (transfer) & 0.00 & 0.03 & 40,735 \\
 & No cause & 0.10 & 0.30 & 40,735 \\
 & No cause (transfer) & 0.01 & 0.08 & 40,735 \\
 & Non-payment of rent & 0.73 & 0.44 & 40,735 \\
 & Non-payment of rent (transfer) & 0.02 & 0.13 & 40,735 \\
\cline{1-5}
\multirow[c]{4}{4cm}{\textit{Panel B: Case Resolution}} & Case defaulted & 0.20 & 0.40 & 40,735 \\
 & Case involuntarily dismissed & 0.29 & 0.45 & 40,735 \\
 & Case heard & 0.06 & 0.23 & 40,735 \\
 & Case mediated & 0.41 & 0.49 & 40,735 \\
\cline{1-5}
\multirow[c]{5}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.09 & 0.28 & 40,735 \\
 & Plaintiff has an attorney & 0.84 & 0.37 & 40,735 \\
 & Defendant is an entity & 0.01 & 0.08 & 40,735 \\
 & Plaintiff is an entity & 0.70 & 0.46 & 40,735 \\
 & Money judgment & 1890.04 & 5279.02 & 40,735 \\
\cline{1-5}
\multirow[c]{5}{4cm}{\textit{Panel D: Assessor Records From Post-Filing F.Y.}} & Total property value & 9435708.78 & 20612629.31 & 14,491 \\
 & Building value & 2482603.38 & 6470958.91 & 14,491 \\
 & Land value & 113817.19 & 536568.37 & 14,491 \\
 & Other value & 12020146.88 & 26285935.89 & 14,491 \\
 & Units & 42.25 & 112.87 & 14,491 \\
\cline{1-5}
\multirow[c]{9}{4cm}{\textit{Panel E: Zestimates Around Last Docket Date}} & Five years before latest docket date & 261403.18 & 249286.93 & 8,865 \\
 & Four years before latest docket date & 280115.12 & 286856.77 & 8,994 \\
 & Three years before latest docket date & 306539.18 & 377212.67 & 9,198 \\
 & Two years before latest docket date & 341425.83 & 1033374.53 & 9,210 \\
 & One year before latest docket date & 350912.11 & 314096.19 & 9,217 \\
 & Latest docket date & 376241.94 & 315819.32 & 9,129 \\
 & One year after latest docket date & 421391.90 & 347409.45 & 9,476 \\
 & Two years after latest docket date & 478657.38 & 468642.16 & 8,363 \\
 & Three years after latest docket date & 503342.65 & 795669.13 & 5,368 \\
\cline{1-5}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llccc}
\toprule
 &  & Mean & S.D. & N \\
Panel & Variable &  &  &  \\
\midrule
\multirow[c]{8}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 0.32 & 40,735 \\
 & For cause (transfer) & 0.01 & 0.08 & 40,735 \\
 & Foreclosure & 0.02 & 0.14 & 40,735 \\
 & Foreclosure (transfer) & 0.00 & 0.03 & 40,735 \\
 & No cause & 0.10 & 0.30 & 40,735 \\
 & No cause (transfer) & 0.01 & 0.08 & 40,735 \\
 & Non-payment of rent & 0.73 & 0.44 & 40,735 \\
 & Non-payment of rent (transfer) & 0.02 & 0.13 & 40,735 \\
\cline{1-5}
\multirow[c]{4}{4cm}{\textit{Panel B: Case Resolution}} & Case defaulted & 0.20 & 0.40 & 40,735 \\
 & Case involuntarily dismissed & 0.29 & 0.45 & 40,735 \\
 & Case heard & 0.06 & 0.23 & 40,735 \\
 & Case mediated & 0.41 & 0.49 & 40,735 \\
\cline{1-5}
\multirow[c]{5}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.09 & 0.28 & 40,735 \\
 & Plaintiff has an attorney & 0.84 & 0.37 & 40,735 \\
 & Defendant is an entity & 0.01 & 0.08 & 40,735 \\
 & Plaintiff is an entity & 0.70 & 0.46 & 40,735 \\
 & Money judgment & 1890.04 & 5279.02 & 40,735 \\
\cline{1-5}
\multirow[c]{5}{4cm}{\textit{Panel D: Assessor Records From Post-Filing F.Y.}} & Total property value & 9435708.78 & 20612629.31 & 14,491 \\
 & Building value & 2482603.38 & 6470958.91 & 14,491 \\
 & Land value & 113817.19 & 536568.37 & 14,491 \\
 & Other value & 12020146.88 & 26285935.89 & 14,491 \\
 & Units & 42.25 & 112.87 & 14,491 \\
\cline{1-5}
\multirow[c]{9}{4cm}{\textit{Panel E: Zestimates Around Last Docket Date}} & Five years before latest docket date & 261450.07 & 238031.93 & 9,843 \\
 & Four years before latest docket date & 280231.05 & 276040.32 & 9,969 \\
 & Three years before latest docket date & 307124.02 & 369747.73 & 10,173 \\
 & Two years before latest docket date & 341068.35 & 987098.31 & 10,183 \\
 & One year before latest docket date & 351156.71 & 311971.28 & 10,191 \\
 & Latest docket date & 377366.88 & 316634.29 & 10,097 \\
 & One year after latest docket date & 421583.49 & 344317.43 & 10,444 \\
 & Two years after latest docket date & 477926.97 & 457674.35 & 9,176 \\
 & Three years after latest docket date & 501586.74 & 780403.17 & 5,895 \\
\cline{1-5}
\bottomrule
\end{tabular}
